Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-28 doc/paper.Rmd
no hashes in latex section
adding ccf entry to table

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
  \textbf{\citet{aoas}} & LEAs \\
Consecutive Matching Bullets Striae (CMS) &  &  6.25\% &  33.85\% \\ 
Consecutive Non-matching Striae (CNMS)  & &  6.26\% & 35.42\%  \\ 
Average Distance (D) &   &   6.25\% & 45.83\% \\ 
Cross-correlation Function (CCF) & &  6.25\% & 17.71\%  \\ 
Sum of Peaks (S) &  &  6.25\% &  18.23\% \\
   \hline
   \textbf{\citet{chu2013}} & LEAs \\
Consecutive Matching Bullets Striae (CMS) &  &  0\% &  52\% \\ 
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source land-to-land analysis reported in the literature.}
\end{table}

@@

```{r type2, fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
if (!file.exists("../data/cvcs2.RDS")) {
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
cvcs2$method <- "CS2"
saveRDS(cvcs2, file = "../data/cvcs2.RDS")
} else cvcs2 <- readRDS("../data/cvcs2.RDS")

@@

>>>>

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
  \textbf{\citet{aoas}} & LEAs \\
Consecutive Matching Bullets Striae (CMS) &  &  6.25\% &  33.85\% \\ 
Consecutive Non-matching Striae (CNMS)  & &  6.26\% & 35.42\%  \\ 
Average Distance (D) &   &   6.25\% & 45.83\% \\ 
Cross-correlation Function (CCF) & &  6.25\% & 17.71\%  \\ 
Sum of Peaks (S) &  &  6.25\% &  18.23\% \\
   \hline
   \textbf{\citet{chu2013}} & LEAs \\
Consecutive Matching Bullets Striae (CMS) &  &  0\% &  52\% \\ 
   \hline
   \textbf{\citet{chu2010}} \& \textbf{\citet{ma2004}} & LEAs \\
Cross-Correlation Function (CCF) &  &  - &  - \\ 
    \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source land-to-land analysis reported in the literature.}
\end{table}

@@

```{r t, echo = FALSE}
if (!file.exists("../data/cvcs2.RDS")) {
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
cvcs2$method <- "CS2"
saveRDS(cvcs2, file = "../data/cvcs2.RDS")
} else cvcs2 <- readRDS("../data/cvcs2.RDS")

@@

\newpage
\section{Type 2 errors: CS1 vs CS2}

\autoref{fig:type2} gives an overview of type 2 error rates of methods CS1 and CS2 for different significance levels $\alpha$. Method CS2 is outperforming CS1 significantly in every instance.

```{r type2, fig.pos = 'h', fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
ggerrors
```
